MSHS COVID-19 Vaccinations

### 2021-10-13 Weekly_Arrivals_Future_Sched_Tracking.Rmd
Update analysis reference file and incorporate dose 3 for MSSN for weekly dashboard.

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-08-16.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-08-16.xlsx"),
                           sheet = "Pod Mappings Simple")

@@

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")
```

@@

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y"),
         VaccWeek = as.numeric(
           floor((ApptDate - vacc_start_first_sun) / 7 +1)),
         Dose3 = NA) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0))

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-09-29.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-09-29.xlsx"),
                           sheet = "Pod Mappings Simple")

@@

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "Dose3", "AllDoses")
```

@@

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y"),
         VaccWeek = as.numeric(
           floor((ApptDate - vacc_start_first_sun) / 7 +1))) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0))
